%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager: Platform Applications} % Job title
    {BlackSky / OpenWhere} % Organization
    {Herndon, VA} % Location
    {August 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architect, developer, and current leader of the Platform Applications team; responsible for all customer-facing web applications at BlackSky.}
        \item {Manager and mentor to a diverse team of 6 individuals of varying skill levels and specializations.}
        \item {Responsible for architecting, programming, and maintaining over a dozen web applications, supporting both external and internal customers.}
        \item {Defined and championed the processes around tracking work, reviewing code, and communicating releases.}
        \item {Liaison for multiple groups within the organization to facilitate the collection, documentation, and prioritization of requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer} % Job title
    {FX Machine} % Organization
    {Oakton, VA} % Location
    {Oct. 2013 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Incorporated a startup focusing on developing proprietary AI/ML-based trading algorithms for financial markets.}
        \item {Despite moderate success, learned that predicting the future is very hard to do, and that it's more cost-effective to simply buy and hold Bitcoin.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer \& Team Lead: iSpatial Project} % Job title
    {Thermopylae Sciences and Technology} % Organization
    {Arlington, VA} % Location
    {Jan. 2011 - Nov. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 6 engineers in the rearchitecture of a PHP-based GIS application to a modern Python/JavaScript implementation.}
        \item {Defined the process around code reviews, repository management, versioning, and releases.}
        \item {Led daily scrums, managed the product backlog, and delivered software at a two-week sprint cadence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Solers} % Organization
    {Arlington, VA} % Location
    {Nov. 2010 - Jan. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded a unit testing and performance metrics endeavor for evaluating different JMS/AMQP message queues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CGI Federal} % Organization
    {Fairfax, VA} % Location
    {Jun. 2009 - Nov. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {One of seven team members in charge of developing FederalReporting.gov, the application responsible for tracking the 2008 ARRA (American Recovery and Reinvestment Act) stimulus package.}
        \item {An extremely high profile project with an extremely tight deadline, the success made national news, and the experience was formative and enlightening with regard to working (with others) in high-pressure circumstances.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
